BIP Architectures and Open pNets

### 2019-01-27 2018-Arch-pNets/arch-pNets.tex
arch-pNets paper: (Minor) Edits to the example of an open transition

\begin{example}\emph{An open-transition.}
  \label{OT:enable-composed}
  The \texttt{Failure TimerMonitor} pNet of \Fig{FailureTimer:pNet} has 2 controllers 
  and 2 holes. One of its possible open-transitions is:\\[-2ex]
%%   \footnote{Note the underlined action notation that we use to represent synchronised actions, i.e. actions that are the result of a synchronisation and that we declare as \emph{non-observable}. Those actions are only used for monitoring purposes and statement of properties but cannot be synchronised again in a synchronisation vector. This allows us to define a weak bisimilarity equivalence with p=compositional properties.}
%%   : 
%% \noteLH{underline notation might be a bit too much for this paper : see at the end if we remove it or not (will we use it?)}
% \smallskip
%$  OT_1  = \openrule
%{\emptyset, \{t:=0, z:=TopInt, zone:=[minZone,maxZone]\} }
%{\ostate{00} \OTarrow{\underline{\alpha_4}} \ostate{11}}
%$
%\medskip
\begin{small}\[ \openrule
  {\{B\mapsto fail(b0)\},\\
    t<GetMax(z) \land b1=true \land b1=>b0 \land z1= (z \cap (b1?zone;TopInt)+t),
    \{z:=z1\} }
  {\ostate{11} \OTarrow{\alpha_0} \ostate{12}}
  \]
\end{small}\vspace{-1.5ex}
%
%The first one, $OT_1$, corresponds to the simultaneous initialisation
%of both controlers. No hole is active at that time, and the resulting
%global action is denoted $\alpha_4$.

It correspond to the firing of the connector
$''tick, fail, fail''$. It states that, if the hole B performs an action $fail$, and the (complex) guard is satisfied, then the variable $z$ is set to $z1$ (as specified by the guard), then the transition below the dotted line occurs and a global action labelled $\alpha_0$ occurs. Only the second pLTS performs a transition from state $1$ to state $2$.

>>>>

\begin{example}[An open-transition]
  \label{OT:enable-composed}
  The \texttt{Failure TimerMonitor} pNet of \Fig{FailureTimer:pNet} has \replaceSB{2 controllers 
  and 2 holes. O}{two coordinators and four dangling ports, which can be grouped into two holes (see \secn{encoding} below).  Disregarding the maximal progress priority, o}ne of its possible open-transitions is:\\[-2ex]
%%   \footnote{Note the underlined action notation that we use to represent synchronised actions, i.e. actions that are the result of a synchronisation and that we declare as \emph{non-observable}. Those actions are only used for monitoring purposes and statement of properties but cannot be synchronised again in a synchronisation vector. This allows us to define a weak bisimilarity equivalence with p=compositional properties.}
%%   : 
%% \noteLH{underline notation might be a bit too much for this paper : see at the end if we remove it or not (will we use it?)}
% \smallskip
%$  OT_1  = \openrule
%{\emptyset, \{t:=0, z:=TopInt, zone:=[minZone,maxZone]\} }
%{\ostate{00} \OTarrow{\underline{\alpha_4}} \ostate{11}}
%$
%\medskip
\begin{small}\[ \openrule
  {\{B\mapsto fail(b0)\},\\
    t<GetMax(z) \land b1=true \land b1=>b0 \land z1= (z \cap (b1?zone;TopInt)+t),
    \{z:=z1\} }
  {\ostate{11} \OTarrow{\alpha_0} \ostate{12}}
  \]
\end{small}\vspace{-1.5ex}
%
%The first one, $OT_1$, corresponds to the simultaneous initialisation
%of both controlers. No hole is active at that time, and the resulting
%global action is denoted $\alpha_4$.

It corresponds to the firing of the \replaceSB{connector
$''tick, fail, fail''$}{interaction $\listset{\NameTimer.\PortTick, \PortFail, \NameCtrl.\PortFail}$}. It states that, if the hole $B$ performs an action $fail$, and the (complex) guard is satisfied, then the variable $z$ is set to $z1$ (as specified by the guard), then the transition below the dotted line occurs and a global action labelled $\alpha_0$ occurs. Only the second pLTS performs a transition from state $1$ to state $2$.
